\documentclass{article}

\usepackage[letterpaper, total={8.5in, 11in}]{geometry}
\usepackage[nodisplayskipstretch]{setspace}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{scrextend}
\usepackage[sfdefault,condensed]{roboto}
\usepackage{qrcode}

\usepackage{ltablex}

\urlstyle{same}

\definecolor{title}{rgb}{ 0,0,0 }
\definecolor{accent}{rgb}{ 0,0,0 }
\definecolor{accentlight}{rgb}{ 0,0,0 }

\newcolumntype{L}{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}X}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\newgeometry{margin=2.25cm}

\setlength\LTpre{0pt}
\setlength{\LTpost}{0pt}

\begin{minipage}[t]{0.55\textwidth}
	\begin{flushleft}
		\vfill \textbf{\Huge{ William Floyd }} \\ \hfill \vfill
	\end{flushleft}
\end{minipage}
  
  
\begin{minipage}[t]{0.40\textwidth}
	\begin{flushright}
  
		\textit{
			\setstretch{1.15}
			\href{tel: +1 (865) 244-9330 }{ +1 (865) 244-9330 } \hspace{1mm}
			  
			\color{accentlight}\faIcon{phone-square}\color{black}
			  
			\\
			\href{mailto: wfloyd@notmy.space }{ wfloyd@notmy.space } \hspace{1mm}
			  
			\color{accentlight}\faIcon{envelope}\color{black}
			  
			\\
			\href{ https://notmy.space }{ https://notmy.space } \hspace{1mm} 
			  
			\color{accentlight}\faIcon{external-link-square-alt}\color{black}
			  
			\\
			\href{ https://github.com/W-Floyd }{ github.com/W-Floyd } \hspace{1mm}
			  
			\color{accentlight}\faIcon{github-square}\color{black}
			  
			\\
			\href{ https://linkedin.com/in/william-floyd }{ linkedin.com/in/william-floyd } \hspace{1mm} 
			  
			\color{accentlight}\faIcon{linkedin}\color{black}
			  
			\\
		}
	\end{flushright}
\end{minipage}
  
  

\textbf{\textcolor{title}{\uppercase{
			 Education 
		}}}  \medskip \\  \hfill
\begin{tabularx}{\textwidth}{R{3.5cm} L}
  
\textcolor{accent}{
      
     May 2022 
      
} &
\textbf{ Mechanical Engineering, B.S. (BSME) } - \textit{ LeTourneau University } \linebreak
GPA:  3.54/4.0 (Cum Laude, Dean's List Fall 2018, President's List Spring 2020)  \\\\ \hfill
  
\end{tabularx}

 

  
\textbf{\textcolor{title}{\uppercase{ Engineering Experience }}}  \medskip \\ \hfill
\begin{tabularx}{\textwidth}{R{3.5cm} L}
	  
\end{tabularx}
  

  
\textbf{\textcolor{title}{\uppercase{ Projects }}}  \medskip \\ \hfill
\begin{tabularx}{\textwidth}{R{3.5cm} L}
	  
	\textcolor{accent}{
		  
		 Fall 2021  ---  Spring 2022 
		  
	} &
	  
	\textbf{\href{ https://letu.edu/academics/engineering/nathan_green_senior_design_team.html }{ LEGRange (Senior Design) }},
	  
	\textit{ <no value> } \linebreak
	 Participating in mechanical design for electronics housing, and SDR development and modification for GPS transmission purposes (using C++). Existing software interprets sampled radio signals and reads GPS data. Primary tasking involves implementing rogue signal generation in software given timing and performance constraints.
                 \\\\ \hfill
	  
	\textcolor{accent}{
		  
		 Fall 2020  ---  Fall 2021 
		  
	} &
	  
	\textbf{ Freshman Project Design Team },
	  
	\textit{ LeTourneau University (LETU) } \linebreak
	 Led design project for the 2021 Introduction to Engineering Practices 1 (IEP 1) class. Design involved PCB layout, SolidWorks modelling, and Arduino integration and programming. Production run of 185 units were sourced and kits collected.
                 \\\\ \hfill
	  
	\textcolor{accent}{
		  
		 October 2020  ---  Present 
		  
	} &
	  
	\textbf{\href{ https://github.com/W-Floyd/ha-mqtt-iot }{ Home Assistant MQTT IOT }},
	  
	\textit{ Personal } \linebreak
	 Open source software that provides a MQTT client to interface with HomeAssistant, a home automation software suite. This tool allows creating arbitrary sensors, switches, lights, etc. based on locally run commands, or builtin routines. Programmed in Golang.
                 \\\\ \hfill
	  
	\textcolor{accent}{
		  
		 Fall 2019 
		  
	} &
	  
	\textbf{\href{ https://notmy.space/2020/03/clickbait/ }{ ClickBait }},
	  
	\textit{ LETU } \linebreak
	 Led an engineering project to create a battery powered automatic fishing caster intended for disabled users, as part of Project Management, Design, and Entrepreneurship.
                 \\\\ \hfill
	  
	\textcolor{accent}{
		  
		 Spring 2019 
		  
	} &
	  
	\textbf{\href{ https://notmy.space/2021/12/pen-plotter/ }{ Pen Plotter }},
	  
	\textit{ LETU } \linebreak
	 For IEP 2 class, designed from scratch a low cost (\$20) CNC pen plotter, including 3D printed hardware and custom GCode parser.
                 \\\\ \hfill
	  
\end{tabularx}

 
 \textbf{\textcolor{title}{\uppercase{ Technical Skills }}}  \medskip \\ \hfill
 \begin{tabularx}{\textwidth}{R{3.5cm} L}
	   
	 \textcolor{accent}{ Office } & \textit{ Microsoft Office suite, Outlook macros, Outlook rules, Autohotkey macros } \\ \hfill
	   
	 \textcolor{accent}{ CAD/3D Modeling } & \textit{ SolidWorks, OpenSCAD, Blender, KiCAD } \\ \hfill
	   
	 \textcolor{accent}{ Programming } & \textit{ Golang, Bash scripting, SQL queries, C++, Octave/MATLAB, LabVIEW } \\ \hfill
	   
	 \textcolor{accent}{ Software Development } & \textit{ Git, Arduino/PlatformIO, MQTT, Appsmith, Airtable/NocoDB } \\ \hfill
	   
	 \textcolor{accent}{ Linux Systems } & \textit{ System administration, Debian, Arch, Docker, Package maintenance } \\ \hfill
	   
	 \textcolor{accent}{ Multimedia } & \textit{ Inkscape, Photoshop, After Effects, LaTeX } \\ \hfill
	   
	 \textcolor{accent}{ Fabrication } & \textit{ Welding (MIG, stick), Lathing, Milling } \\ \hfill
	   
	 \textcolor{accent}{ Prototyping } & \textit{ 3D Printing (FDM), Soldering, Electronics Design, Basic PCB layout } \\ \hfill
	   
 \end{tabularx}
 
  
 \textbf{\textcolor{title}{\uppercase{ Leadership Experience }}}  \medskip \\ \hfill
 \begin{tabularx}{\textwidth}{R{3.5cm} L}
	   
 \end{tabularx}
   
 
   
 
 \end{document}
 